\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-05 fully-abstract-comp/popl2019/paper.tex
Outline for FAOS section.

@@

\begin{itemize}
\item present our source language, its operational semantics (excerpts)
\item tell more about components, specifically well-formed according to judgement
\item mention our assumption of reasonability
\item present the full abstraction theorem.
\end{itemize}

>>>>

The overlay semantics we define for \trgcm{} (\srccm{}) is defined in Figure~\ref{fig:src-syntax} and \ref{fig:src-op-sem}.
The main things it adds to \trgcm{} is a built-in stack that can be used to store local state as well as a \texttt{call} instruction and a new interpretation of \texttt{xjmp} that corresponds to returning.
% Describe the things added to the syntax
% Built-in stack
% Stack pointer
% Return pointers

@@

% Describe the changes to op sem
% Step relation change, call case and global constants
% Call semantics
% New xjmp semantics (can be defined in terms of a new xjmpresult function!)
% Example of alternative interpretation for the new syntactic constructs

% Well-formed components

% Reasonability

% Full abstraction thm

% \begin{itemize}
% \item present our source language, its operational semantics (excerpts)
% \item tell more about components, specifically well-formed according to judgement
% \item mention our assumption of reasonability
% \item present the full abstraction theorem.
% \end{itemize}
